|

### 2023-05-09 paper/04-results.Rmd
more results writing

[^crosbysack]: An real-game footage of this play is available at https://www.raiders.com/video/de-maxx-crosby-sacks-qb-teddy-bridgewater-for-a-loss-of-6-yards-nfl

@@

@@

unsuccessful pass rush play: https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb

Figure \ref{fig:fig_crosby_curves_unsucess}

@@

Our results show many true positives with no surprises. Myles Garrett and TJ Watt are known as top-tier edge rushers, while Aaron Donald is undoubtedly the best interior defender in football. Rashan Gary, a young rusher with huge potential, ranks first among all pass-rushers according to our metric. Our leaderboards largely match the rankings of experts in the field (for instance, PFF's edge and interior rusher rankings after the 2021 season), lending credibility to our proposed metric as a measure of pass-rushing effectiveness.

https://www.pff.com/news/nfl-2022-edge-rusher-rankings-tiers

https://www.pff.com/news/nfl-interior-defensive-line-rankings-tiers-2022

@@

Next, we examine the predictability of STRAIN as a measure of pressure.
We first look at how well strain correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} shows a scatterplot of average STRAIN and pressure rate.
We observe a fairly strong correlation (r = 0.625)...

Furthermore, first 4 weeks’ avg STRAIN is more predictive of last 4 weeks’ hurries sacks hits rate than first 4 weeks’ HSH rate

(INSERT FIGURE)

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Corr with pressure rate = (hits + sacks + hurries) per snap"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

@@

Figure \ref{fig:fig_stability} is a scatterplot of average STRAIN across all frames played in first and last 4 weeks.
It is apparent that there is a strong correlation (r = 0.854), illustrating great metric stability over time.

Figure \ref{fig:fig_predictability} (0.09651732 vs 0.3216974)

>>>>

@@

In contrast, Figure \ref{fig:fig_crosby_curves_unsucess} shows the feature curves for an unsuccessful pass rush attempt by the Raiders defense from the same game.
In this play, Broncos QB Teddy Bridgewater is well-protected by the offensive line and is able to release a long pass[^unsuccess].
We see that the STRAIN generated by Crosby and other pass rushers are relative small for this play, compared to the previous play which resulted in a sack.

[^unsuccess]: https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb

@@

@@

Our results show many true positives with no surprises. Myles Garrett and TJ Watt are known as top-tier edge rushers, while Aaron Donald is undoubtedly the best interior defender in football. Rashan Gary, a young rusher with huge potential, ranks first among all pass-rushers according to our metric. Our leaderboards largely match the rankings of experts in the field -- for instance, PFF's edge [@Monson2022nfl] and interior [@Linsey2022nfl] rusher rankings after the 2021 season, lending credibility to our proposed metric as a measure of pass-rushing effectiveness.

@@

some sentences

Next, we examine the predictability of STRAIN as a measure of pressure.
We first look at how well strain correlates with a simple measure of pressure rate, defined as the total hits, sacks and hurries per snap.
Figure \ref{fig:fig_cor_pressure} is a scatterplot of average STRAIN and pressure rate which reveals a fairly strong correlation (r = 0.625) between the quantities.
Note that we only consider players with at least 100 snaps played.
Furthermore, the average STRAIN for the first 4 weeks of the 2021 season is more predictive of the last 4 weeks' pressure rate ($r=0.322$) than the first 4 weeks' pressure rate ($r=0.097$), as illustrated in Figure \ref{fig:fig_predictability}.

We also examine the stability of STRAIN over time by comparing the average STRAIN across all frames played in first and last four weeks of the 2021 NFL regular season.
It is apparent from Figure \ref{fig:fig_stability} that there is a strong correlation $(r = 0.854)$ for this relationship, illustrating that STRAIN is a stable quantity over the provided 8-week window.

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Relationship between  with pressure rate = (hits + sacks + hurries) per snap"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

@@
